---
title: "Panel Network"
author: "Anna Langener"
date: "7/9/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup}
library("qgraph")
library("dplyr")
library("psych")
library("graphicalVAR")
library("psychonetrics")
library("lavaan")
library('ltm')
library("semPlot")
library('tidyr')
library('ggplot2')
library("ggcorrplot")
library("readxl")
library("IsingFit")
library("bootnet")
library("flextable")
library("psych")
library("kableExtra")
library("tidyverse")
library("tidyselect")
library("xtable")
library("qwraps2")
library("lme4")
library("lmerTest")
library("readxl")
library("ggpubr")

### Load combined dataset
All_Rwanda_complete <- as.data.frame(read.csv("/Users/annalangener/surfdrive/Data Thesis/Data Final Thesis/All_Rwanda_complete_11.07.csv", header = TRUE, na.strings = c(""," ","NA")))
```


## Function to count variables
I just used this function to count how many participants and groups we have for each variable and wave of measurement. 

```{r setup, include=FALSE}
# Function to count observations per variable per time point

counting_obs2 <- function(round, variable) {
  counter <- 0
  dataset <- All_Rwanda[All_Rwanda$Rround == round,]
  if(nrow(dataset)!= 0) {
  index <- which(colnames(dataset) == variable)
  print(index)
  for(i in 1:nrow(dataset)){
    if(is.na(dataset[i, as.numeric(index)]) == F)
      {
      counter <- counter + 1
    }
  }
  result <- counter
  }else{
  result <- 0
  }
  return(result)
}


counting_function <- function(variable) {
round_list <- c(0,1,2,3,4,5,6,7,8)
result <- as.data.frame(matrix(0, nrow = length(variable_list), ncol = 11))
colnames(result) <- c("variable", "O","1","2", "3", "4", "5", "6", "7", "8")
for(i in 1:length(variable_list)){
      for(j in 1:length(round_list)){
        result$variable[i] <- variable_list[i]
        result[i,j + 1] <- counting_obs2(round = round_list[j], variable = variable_list[i])
  }
}
  return(result)
}

## choose variable
All_Rwanda <- All_Rwanda_complete[!is.na(All_Rwanda_complete$Rgroupnr),]

variable_list <- colnames(All_Rwanda)
counting <- counting_function(variable = variable_list)

openxlsx::write.xlsx(counting, "Overview2.xlsx")

### Adapted function to cound the groups per variable per time point

counting_obs2 <- function(round, variable) {
  counter <- 0
  dataset <- All_Rwanda_complete[All_Rwanda_complete$Rround == round,]
  if(nrow(dataset)!= 0) {
  index <- which(colnames(dataset) == variable)
  print(index)
  dataset <- na.omit(dataset[,c(as.numeric(index),4)])
  counter <- length(unique(dataset$Rgroupnr))
  print(counter)
  result <- counter
  }else{
  result <- 0
  }
  return(result)
}

counting_function <- function(variable) {
round_list <- c(0,1,2,3,4,5,6,7,8)
result <- as.data.frame(matrix(0, nrow = length(variable_list), ncol = 11))
colnames(result) <- c("variable", "O","1","2", "3", "4", "5", "6", "7", "8")
for(i in 1:length(variable_list)){
      for(j in 1:length(round_list)){
        result$variable[i] <- variable_list[i]
        result[i,j + 1] <- counting_obs2(round = round_list[j], variable = variable_list[i])
  }
}
  return(result)
}

## choose variable
All_Rwanda <- All_Rwanda_complete[!is.na(All_Rwanda_complete$Rgroupnr),]

variable_list <- colnames(All_Rwanda)
counting <- counting_function(variable = variable_list)

```

## Create Scale Scores
Here I just create scale scoles, for the plot, descriptive analysis, and robustness check.
```{r}
### Create sum scores (for the plot and the descriptives)
#Psychwellbeing
index <- which(colnames(All_Rwanda_complete) %in% c("psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_4","psychwellbeing_5","psychwellbeing_6","psychwellbeing2_1", "psychwellbeing2_2","psychwellbeing2_3","psychwellbeing2_4","psychwellbeing2_5","psychwellbeing2_6"))

All_Rwanda_complete$PsychologicalWellbeingScaleFull <- rowSums(All_Rwanda_complete[,index])

index <- c("psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5")

All_Rwanda_complete$PsychologicalWellbeingScale <- rowSums(All_Rwanda_complete[,index])


#Social Support
index <- which(colnames(All_Rwanda_complete) %in% c("socialsupport_1","socialsupport_2","socialsupport_3","socialsupport_4"))
All_Rwanda_complete$SocialSupportScaleFull <- rowSums(All_Rwanda_complete[,index])


#Empowerment
index <- which(colnames(All_Rwanda_complete) %in% c("decisionmaking_1","decisionmaking_2","decisionmaking_4","decisionmaking_3","hermoney","hismoney","hhpurchases","decisionfam"))
All_Rwanda_complete$EmpowermentScaleFull <- rowSums(All_Rwanda_complete[,index])

index <- which(colnames(All_Rwanda_complete) %in% c("hermoney","hhpurchases"))
All_Rwanda_complete$EmpowermentScale <- rowSums(All_Rwanda_complete[,index])


#Stereotypes
index <- which(colnames(All_Rwanda_complete) %in% c("stereotypes_1","stereotypes_2","stereotypes_3","stereotypes_4"))
All_Rwanda_complete$StereotypesScaleFull <- rowSums(All_Rwanda_complete[,index])
```

Test wheather old groups have higher wellbeing (impact corona)

```{r setup, include=FALSE}
All_Rwanda_complete$IndexG[is.na(All_Rwanda_complete$IndexG)] <- 0
NewGroups <- All_Rwanda_complete[All_Rwanda_complete$IndexG == 1,]
OldGroups <- All_Rwanda_complete[All_Rwanda_complete$IndexG == 0,]

t.test(NewGroups$PsychologicalWellbeingScale,OldGroups$PsychologicalWellbeingScale)

```


## Correlation Plot
```{r}
All_Rwanda_complete$average_totalinc_without
### Correlation
library(apaTables)

All_Rwanda_complete$Rround[All_Rwanda_complete$Rround == 100] <- 8


All_Rwanda_complete[All_Rwanda_complete$IndexG == 1,] %>% dplyr::select("PsychologicalWellbeingScaleFull","EmpowermentScaleFull", "SocialSupportScaleFull","StereotypesScaleFull","average_totalinc_without","InflationAverage_totalinc_without", "Rround") %>%  apa.cor.table(., filename="Table1_APA.doc", table.number= NA, show.conf.interval = F, landscape = FALSE)


All_Rwanda_complete %>% dplyr::select( "PsychologicalWellbeingScale", "EmpowermentScale","average_totalinc_without","InflationAverage_totalinc_without", "Rround") %>%  apa.cor.table(., filename="Table1_APA.doc", table.number=NA,  show.conf.interval = FALSE, landscape = FALSE)

```


## Plot of average Scale Score over time
```{r}
# Plot average change in variables
index1 <- c(0,1,2,3,4,5,6,7,8)
Rround <- numeric()
AveragePsychologicalWellbeingScaleFull <- numeric()
AverageEmpowermentScaleFull  <- numeric()
AveragePsychologicalWellbeingScale <- numeric()
AverageEmpowermentScale  <- numeric()
AverageSocialSupportScaleFull <- numeric()
AverageStereotypesScaleFull  <- numeric()
InflationAverage_totalinc_without1 <- numeric()
InflationAverage_totalinc_without2 <- numeric()

counter <- 0
ID_NR_VU <- numeric()

for(k in 1:length(index1)){
counter <- counter + 1
Plot <- All_Rwanda_complete[All_Rwanda_complete$IndexG == 1,]
Plot <- All_Rwanda_complete[All_Rwanda_complete$Rround == index1[k],]


AveragePsychologicalWellbeingScale[counter] <- mean(Plot$PsychologicalWellbeingScale, na.rm =  T)

AverageEmpowermentScale[counter]  <- mean(Plot$EmpowermentScale,  na.rm =  T)

InflationAverage_totalinc_without1[counter]  <- mean(Plot$InflationAverage_totalinc_without,  na.rm =  T)
}

counter <- 0


for(k in 1:length(index1)){
counter <- counter + 1
Plot <- All_Rwanda_complete[All_Rwanda_complete$Rround == index1[k],]


AveragePsychologicalWellbeingScaleFull[counter] <- mean(Plot$PsychologicalWellbeingScaleFull, na.rm =  T)

AverageEmpowermentScaleFull[counter]  <- mean(Plot$EmpowermentScaleFull,  na.rm =  T)

AverageSocialSupportScaleFull[counter] <- mean(Plot$SocialSupportScaleFull,  na.rm =  T)

AverageStereotypesScaleFull[counter]  <- mean(Plot$StereotypesScaleFull,  na.rm =  T)
}


Group_average <- as.data.frame(cbind(index1,AveragePsychologicalWellbeingScaleFull, AveragePsychologicalWellbeingScale,  AverageEmpowermentScaleFull, AverageEmpowermentScale, AverageSocialSupportScaleFull, AverageStereotypesScaleFull, InflationAverage_totalinc_without1, InflationAverage_totalinc_without2))

figure1 <- ggplot(Group_average, x = index1) +
  geom_bar(stat="identity", aes(index1,AveragePsychologicalWellbeingScaleFull)) +
  ylab("Psychological Wellbeing") +
  xlab("Round")
   
figure2 <- ggplot(Group_average, x = index1) +
   geom_bar(stat="identity",aes(index1,AverageEmpowermentScaleFull))  +
  ylab("Empowerment") +
  xlab("Round")
  
figure3 <- ggplot(Group_average, x = index1) +
   geom_bar(stat="identity",aes(index1,AveragePsychologicalWellbeingScale,)) +
  ylab("Psychological Wellbeing Short") +
  xlab("Round")

figure4 <- ggplot(Group_average, x = index1) +
   geom_bar(stat="identity",aes(index1,AverageEmpowermentScale)) +
  ylab("Empowerment Short") +
  xlab("Round")
  
figure5 <- ggplot(Group_average, x = index1) +
   geom_bar(stat="identity",aes(index1,AverageSocialSupportScaleFull)) +
  ylab("Social Support") +
  xlab("Round")
  
figure6 <- ggplot(Group_average, x = index1) +
   geom_bar(stat="identity",aes(index1,AverageStereotypesScaleFull))  +
  ylab("Stereotypes") +
  xlab("Round")

figure7 <- ggplot(Group_average, x = index1) +
   geom_bar(stat="identity",aes(index1,InflationAverage_totalinc_without1))  +
  ylab("Income") +
  xlab("Round")

figure8 <- ggplot(Group_average, x = index1) +
   geom_bar(stat="identity",aes(index1,InflationAverage_totalinc_without2))  +
  ylab("Income") +
  xlab("Round")

### Full Sample

figure9 <- ggarrange(figure3, figure4, figure7, common.legend = TRUE,legend = "bottom",  ncol = 2, nrow =4)

png('Descriptive Main Variables1.png',height = 20, width = 20, units = 'cm', res = 600)
plot(figure9)
dev.off()


### Sub Sample


figure10 <- ggarrange(figure1, figure2, figure5, figure6, common.legend = TRUE,legend = "bottom",  ncol = 2, nrow =4)

png('Descriptive Main Variables2.png',height = 20, width = 20, units = 'cm', res = 600)
plot(figure10)
dev.off()

```

## Cronbach's Alpha

```{r}
#### Cronbachs Alpha

#Wellbeing Long
All_Rwanda_complete %>% dplyr::select("psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_4","psychwellbeing_5","psychwellbeing_6","psychwellbeing2_1", "psychwellbeing2_2","psychwellbeing2_3","psychwellbeing2_4","psychwellbeing2_5","psychwellbeing2_6") %>% na.omit() %>% cronbach.alpha()

All_Rwanda_complete[All_Rwanda_complete$IndexG == 1,] %>%  dplyr::select("psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_4","psychwellbeing_5","psychwellbeing_6","psychwellbeing2_1", "psychwellbeing2_2","psychwellbeing2_3","psychwellbeing2_4","psychwellbeing2_5","psychwellbeing2_6") %>% apa.cor.table(., filename="Table1_APA.doc", table.number=NA,  show.conf.interval = FALSE, landscape = T)



#Wellbeing Short
All_Rwanda_complete %>% dplyr::select("psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5") %>% na.omit() %>% cronbach.alpha()

#Empowerment Long
All_Rwanda_complete %>% dplyr::select("decisionmaking_1","decisionmaking_2","decisionmaking_4","decisionmaking_3","hermoney","hismoney","hhpurchases","decisionfam") %>% na.omit() %>% cronbach.alpha()

#Empowerment short
All_Rwanda_complete %>% dplyr::select("hermoney","hhpurchases") %>% na.omit() %>% cronbach.alpha()

#Stereotypes short
All_Rwanda_complete %>% dplyr::select("stereotypes_1","stereotypes_2","stereotypes_3","stereotypes_4") %>% na.omit() %>% cronbach.alpha()

All_Rwanda_complete %>% dplyr::select("socialsupport_1","socialsupport_2","socialsupport_3","socialsupport_4") %>% na.omit() %>% cronbach.alpha()

```


### Structural Equation Modeling
Model 1 (Full Sample)
```{r}
# Select Variables 
All_Rwanda_network <- All_Rwanda_complete %>%  dplyr::select("ID_NR_VU","Rround","hermoney","hhpurchases","psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5", "InflationAverage_totalinc_without", "age_1")

All_Rwanda_network$Rround[All_Rwanda_network$Rround == 100] <- 8


All_Rwanda_network[,-1] <- scale(All_Rwanda_network[-1], center = F) #Otherwise model did not converge

Model_SEM <- '
   # Latent variables
   Empowerment =~ hermoney + hhpurchases
   Mental_wellbeing =~ psychwellbeing_1 + psychwellbeing_2 + psychwellbeing_3 + psychwellbeing_5
   
   # Regressions
    InflationAverage_totalinc_without ~ Rround
    Empowerment ~ InflationAverage_totalinc_without + Rround
    Mental_wellbeing ~ InflationAverage_totalinc_without + Empowerment + Rround
'

# Fit in lavaan:
fit2 <- lavaan::sem(Model_SEM, data = All_Rwanda_network, ordered=c("hermoney", "hhpurchases" ,"psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5"))

parameterEstimates(fit2)

fitMeasures(fit2, c("rmsea","cfi","tli","nfi","rfi","ifi","srmr","gfi", "chisq",
"pvalue"))

summary(fit2)



semPaths(fit2,
style = "lisrel", # This will plot residuals as arrows, closer to what we use in c
what = "est",
#residScale = 8, # This makes the residuals larger
reorder = T, # This disables the default reordering
legend.cex = 2, # Makes the legend smaller
layout = "tree2", # tree layout options are "tree", "tree2", and "tree3"
curvePivot = TRUE, # Changes curve into rounded straight lines
sizeMan = 7, # Size of manifest variables
sizeLat = 15, # Size of latent variables
#mar = c(20,5,20,5), # Figure margins
#color = list(lat = c('darkolivegreen2', 'lightblue2','lightsalmon2')),
#nCharNodes = 0,
edge.label.cex = 1,
intercepts = FALSE
)
```

Model 1 (Fullsample, unadjusted income)
```{r}
# Select Variables 
All_Rwanda_network <- All_Rwanda_complete %>%  dplyr::select("ID_NR_VU","Rround","hermoney","hhpurchases","psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5", "average_totalinc_without", "age_1", "Cstartdate")

All_Rwanda_network$Rround[All_Rwanda_network$Rround == 100] <- 8


All_Rwanda_network[,-1] <- scale(All_Rwanda_network[-1], center = F) #Otherwise model did not converge

Model_SEM <- '
   # Latent variables
   Empowerment =~ hermoney + hhpurchases
   Mental_wellbeing =~ psychwellbeing_1 + psychwellbeing_2 + psychwellbeing_3 + psychwellbeing_5
   
   # Regressions
    average_totalinc_without ~ Rround
    Empowerment ~ average_totalinc_without + Rround
    Mental_wellbeing ~ average_totalinc_without + Empowerment + Rround
'

# Fit in lavaan:
fit2 <- lavaan::sem(Model_SEM, data = All_Rwanda_network, ordered=c("hermoney", "hhpurchases" ,"psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5"))

parameterEstimates(fit2)

fitMeasures(fit2, c("rmsea","cfi","tli","nfi","rfi","ifi","srmr","gfi", "chisq",
"pvalue"))

summary(fit2)



semPaths(fit2,
style = "lisrel", # This will plot residuals as arrows, closer to what we use in c
what = "est",
#residScale = 8, # This makes the residuals larger
reorder = T, # This disables the default reordering
legend.cex = 2, # Makes the legend smaller
layout = "tree2", # tree layout options are "tree", "tree2", and "tree3"
curvePivot = TRUE, # Changes curve into rounded straight lines
sizeMan = 7, # Size of manifest variables
sizeLat = 15, # Size of latent variables
#mar = c(20,5,20,5), # Figure margins
#color = list(lat = c('darkolivegreen2', 'lightblue2','lightsalmon2')),
#nCharNodes = 0,
edge.label.cex = 1,
intercepts = FALSE
)
```


Model 2 (Subsample)
```{r}
# Select Variables 

All_Rwanda_network <- All_Rwanda_complete[All_Rwanda_complete$IndexG == 1,] %>%  dplyr::select("ID_NR_VU","Rround","socialsupport_1","socialsupport_2","socialsupport_3","socialsupport_4","decisionmaking_1","decisionmaking_2","decisionmaking_4","decisionmaking_3","hermoney","hismoney","hhpurchases","decisionfam","psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_4","psychwellbeing_5","psychwellbeing_6","psychwellbeing2_1", "psychwellbeing2_2","psychwellbeing2_3","psychwellbeing2_4","psychwellbeing2_5","psychwellbeing2_6")

All_Rwanda_network <- na.omit(All_Rwanda_network)
A
All_Rwanda_network$Rround[All_Rwanda_network$Rround == 8] <- 1

All_Rwanda_network[,2:26] <-  scale(All_Rwanda_network[,2:26], center = F)


#Model without social support_2 hermoney because correlation almost 1


Model_SEM <- '
 # Latent variables
   Empowerment =~ decisionmaking_1 + decisionmaking_2 + decisionmaking_4 + decisionmaking_3 + hhpurchases + hismoney 
   
   Mental_wellbeing =~ psychwellbeing_1 + psychwellbeing_3 + psychwellbeing_4 + psychwellbeing_5 + psychwellbeing_6 + psychwellbeing2_1 + psychwellbeing2_2 + psychwellbeing2_3 + psychwellbeing2_4 + psychwellbeing2_5 + psychwellbeing2_6
   
 SocialSupport =~ socialsupport_1  + socialsupport_3 + socialsupport_4


# Regressions
    SocialSupport ~ Rround
    Empowerment ~ SocialSupport + Rround 
    Mental_wellbeing ~ SocialSupport + Empowerment + Rround
'

# Fit in lavaan:
fit3 <- lavaan::sem(Model_SEM, data = All_Rwanda_network, ordered = c("socialsupport_1" , "socialsupport_3" , "socialsupport_4", "decisionmaking_1","decisionmaking_2","decisionmaking_4","decisionmaking_3","hismoney","hhpurchases","decisionfam", "psychwellbeing_1", "psychwellbeing_2", "psychwellbeing_3","psychwellbeing_4","psychwellbeing_5","psychwellbeing_6","psychwellbeing2_1", "psychwellbeing2_2","psychwellbeing2_3","psychwellbeing2_4","psychwellbeing2_5","psychwellbeing2_6"))
semPaths(fit3)


parameterEstimates(fit3)

fitMeasures(fit3, c("rmsea","cfi","tli","nfi","rfi","ifi","srmr","gfi", "chisq",
"pvalue"))

summary(fit3, standardized = TRUE)

graph_sem(fit3,
          rect_width = 1.2,
  rect_height = 0.8,
  ellipses_width = 2,
  ellipses_height = 2,
  variance_diameter = 0.8,
  spacing_x = 2,
  spacing_y = 2,
  text_size = 4,
  curvature = 60)


semPaths(fit3,
style = "lisrel", # This will plot residuals as arrows, closer to what we use in c
what = "est",
#residScale = 8, # This makes the residuals larger
#reorder = FALSE, # This disables the default reordering
#legend.cex = 2, # Makes the legend smaller
layout = "tree2", # tree layout options are "tree", "tree2", and "tree3"
#cardinal = "lat cov", # This makes the latent covariances connet at a cardinal cen
#curvePivot = TRUE, # Changes curve into rounded straight lines
#sizeMan = 7, # Size of manifest variables
#sizeLat = 15, # Size of latent variables
#mar = c(20,5,20,5), # Figure margins
#color = list(lat = c('darkolivegreen2', 'lightblue2','lightsalmon2')), nCharEdges = 0,
#nCharNodes = 0,
#edge.label.cex = 1,
#label.cex = c(1,1,1, 1,1,1, 1,1,1, 1,1.1,.6),
intercepts = FALSE
)



```


Model 3 (Subsample, Stereotypes included)
```{r}
# Select Variables 
All_Rwanda_network <- All_Rwanda_complete %>%  dplyr::select("ID_NR_VU","Rround","socialsupport_1","socialsupport_2","socialsupport_3","socialsupport_4","decisionmaking_1","decisionmaking_2","decisionmaking_4","decisionmaking_3","hermoney","hismoney","hhpurchases","decisionfam","psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_4","psychwellbeing_5","psychwellbeing_6","psychwellbeing2_1", "psychwellbeing2_2","psychwellbeing2_3","psychwellbeing2_4","psychwellbeing2_5","psychwellbeing2_6", "stereotypes_1","stereotypes_2","stereotypes_3","stereotypes_4")

All_Rwanda_network <- na.omit(All_Rwanda_network)
A

All_Rwanda_network$Rround[All_Rwanda_network$Rround == 8] <- 1 #Baseline is 0, Endline is 1

All_Rwanda_network[,2:30] <-  scale(All_Rwanda_network[,2:30], center = F)


#Model without social support_2 hermoney because correlation almost 1

Model_SEM <- '
 # Latent variables
   Empowerment =~ decisionmaking_1 + decisionmaking_2 + decisionmaking_4 + decisionmaking_3 + hhpurchases + hismoney 
   
   Mental_wellbeing =~ psychwellbeing_1 + psychwellbeing_3 + psychwellbeing_4 + psychwellbeing_5 + psychwellbeing_6 + psychwellbeing2_1 + psychwellbeing2_2 + psychwellbeing2_3 + psychwellbeing2_4 + psychwellbeing2_5 + psychwellbeing2_6
   
 SocialSupport =~ socialsupport_1 + socialsupport_2 + socialsupport_3 + socialsupport_4
 
 Stereotypes =~ stereotypes_1 + stereotypes_3 + stereotypes_4

# Regressions
    SocialSupport ~ Rround
    Empowerment ~ SocialSupport + Rround + Stereotypes
    Mental_wellbeing ~ SocialSupport + Empowerment + Rround + Stereotypes
    Stereotypes ~  Rround + SocialSupport
'



# Fit in lavaan:
fit3 <- lavaan::sem(Model_SEM, data = All_Rwanda_network, ordered = c("socialsupport_1" , "socialsupport_3" , "socialsupport_4", "decisionmaking_1","decisionmaking_2","decisionmaking_4","decisionmaking_3","hismoney","hhpurchases","decisionfam", "psychwellbeing_1", "psychwellbeing_2", "psychwellbeing_3","psychwellbeing_4","psychwellbeing_5","psychwellbeing_6","psychwellbeing2_1", "psychwellbeing2_2","psychwellbeing2_3","psychwellbeing2_4","psychwellbeing2_5","psychwellbeing2_6", "stereotypes_1","stereotypes_2","stereotypes_3","stereotypes_4"))
semPaths(fit3)


parameterEstimates(fit3)

fitMeasures(fit3, c("rmsea","cfi","tli","nfi","rfi","ifi","srmr","gfi", "chisq",
"pvalue"))

summary(fit3, standardized = TRUE)


semPaths(fit3,
style = "lisrel", # This will plot residuals as arrows, closer to what we use in c
what = "est",
#residScale = 8, # This makes the residuals larger
#reorder = FALSE, # This disables the default reordering
#legend.cex = 2, # Makes the legend smaller
layout = "tree2", # tree layout options are "tree", "tree2", and "tree3"
#cardinal = "lat cov", # This makes the latent covariances connet at a cardinal cen
#curvePivot = TRUE, # Changes curve into rounded straight lines
#sizeMan = 7, # Size of manifest variables
#sizeLat = 15, # Size of latent variables
#mar = c(20,5,20,5), # Figure margins
#color = list(lat = c('darkolivegreen2', 'lightblue2','lightsalmon2')), nCharEdges = 0,
#nCharNodes = 0,
#edge.label.cex = 1,
#label.cex = c(1,1,1, 1,1,1, 1,1,1, 1,1.1,.6),
intercepts = FALSE
)



```



## Panel Data Network

All time points negative autocorrelation
Only full waves negative correlation
Remove waves with low sample size: # Round 6 smallest sample, round 7, round 2
Without Round 6 no between subject network
Without round 2 and 6 negative autocorrelation
Without round 7 and 6 (no negative autocorrelation, best model so far)
Without round 2, 7 and 6 negative autocorrelation

# Income ajusted for Inflation
```{r setup, include=FALSE}
All_Rwanda_network <- All_Rwanda_complete %>%  dplyr::select("ID_NR_VU","Rround","InflationAverage_totalinc_without","hermoney","hhpurchases", "psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5")
All_Rwanda_network <- All_Rwanda_network[!All_Rwanda_network$ID_NR_VU == 9999,]
All_Rwanda_network <- All_Rwanda_network[!is.na(All_Rwanda_network$ID_NR_VU),]


#Get data into wide format
Empowerment_wide <- reshape(All_Rwanda_network, direction = "wide", timevar = "Rround", idvar = "ID_NR_VU")

Empowerment_wide[,-1] <- scale(Empowerment_wide[,-1], center = F)

colnames(Empowerment_wide)
paste(colnames(Empowerment_wide[-1]), collapse = c("','"))


#Build Design Matrix:
#Each column contains wave of measurement and each row contains variable name. The matrix is then filled with the actual variable names (See summary statitic example)

##Without round 7 and 6 (no negative autocorrelation, best model so far)

varMat1 <- matrix(c('InflationAverage_totalinc_without.0','hermoney.0','hhpurchases.0','psychwellbeing_1.0','psychwellbeing_2.0','psychwellbeing_3.0','psychwellbeing_5.0',
                    'InflationAverage_totalinc_without.1',NA,NA,'psychwellbeing_1.1','psychwellbeing_2.1','psychwellbeing_3.1','psychwellbeing_5.1',
                    'InflationAverage_totalinc_without.2','hermoney.2','hhpurchases.2',NA,NA,NA,NA,
                    'InflationAverage_totalinc_without.3','hermoney.3','hhpurchases.3',NA,NA,NA,NA,
                    'InflationAverage_totalinc_without.4','hermoney.4','hhpurchases.4','psychwellbeing_1.4','psychwellbeing_2.4','psychwellbeing_3.4','psychwellbeing_5.4',
                    'InflationAverage_totalinc_without.5','hermoney.5','hhpurchases.5','psychwellbeing_1.5','psychwellbeing_2.5','psychwellbeing_3.5','psychwellbeing_5.5',
                    'InflationAverage_totalinc_without.8','hermoney.8','hhpurchases.8','psychwellbeing_1.8','psychwellbeing_2.8','psychwellbeing_3.8','psychwellbeing_5.8'),7,7, byrow = F) 


rownames(varMat1) <- c("Income", "hermoney", "hhpurchases","psychwellbeing_1", "psychwellbeing_2", "psychwellbeing_3", "psychwellbeing_5")

#Model 1
model <- panelgvar(data = Empowerment_wide,
  vars = varMat1, estimator = "FIML", missing = "pairwise")

# Run model:
model <- model %>% runmodel

# Check fit:
model %>% fit 

# Estimation algorithm (prune step):
model_prune <- model %>% prune(alpha = 0.05, recursive = FALSE)

##Stepup
model_pruneSP <- model_prune %>%  stepup(alpha = 0.05, criterion = "bic")

model_pruneSP %>% fit


# Compare:
comp <- compare(
  original = model,
  pruned = model_pruneSP
  )

# Differences:
comp$AIC[1] 
comp$AIC[2]

comp$BIC[1]
comp$BIC[2]

temporal <- getmatrix(model_pruneSP, "PDC")
contemporaneous <- getmatrix(model_pruneSP, "omega_zeta_within")
between <- getmatrix(model_pruneSP, "omega_zeta_between")



# Average layout:
Layout <- averageLayout(temporal,contemporaneous,between)


# Plot all graphs:
max <- max(c(abs(temporal),abs(contemporaneous),abs(between)))


fig1 <- qgraph(temporal, labels = c("Income", "hermoney", "hhpurchases","WB_1", "WB_2", "WB_3", "WB_5"), title = "Temporal", label.cex = 1, layout = Layout)
fig2 <- qgraph(contemporaneous, labels = c("Income", "hermoney", "hhpurchases","WB_1", "WB_2", "WB_3", "WB_5"), title = "Contemporaneous",label.cex = 1, layout = Layout)
fig3 <-qgraph(between,labels = c("Income", "hermoney", "hhpurchases","WB_1", "WB_2", "WB_3", "WB_5"), title = "Between Subjects",label.cex = 1, layout = Layout)


png('temporal.png',height = 10, width = 7, units = 'cm', res = 600)
plot(fig1)
dev.off()


png('contemporaneous.png',height = 10, width = 7, units = 'cm', res = 600)
plot(fig2)
dev.off()


png('between.png',height = 10, width = 7, units = 'cm', res = 600)
plot(fig3)
dev.off()

```


# Income not adjusted for Inflations
```{r setup, include=FALSE}
set.seed(12361488)
All_Rwanda_network <- All_Rwanda_complete %>%  dplyr::select("ID_NR_VU","Rround","average_totalinc_without","hermoney","hhpurchases", "psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5")
All_Rwanda_network <- All_Rwanda_network[!All_Rwanda_network$ID_NR_VU == 9999,]
All_Rwanda_network <- All_Rwanda_network[!is.na(All_Rwanda_network$ID_NR_VU),]



#Get data into wide format
Empowerment_wide <- reshape(All_Rwanda_network, direction = "wide", timevar = "Rround", idvar = "ID_NR_VU")

Empowerment_wide[,-1] <- scale(Empowerment_wide[,-1], center = F)

colnames(Empowerment_wide)
paste(colnames(Empowerment_wide[-1]), collapse = c("','"))


#Build Design Matrix:
#Each column contains wave of measurement and each row contains variable name. The matrix is then filled with the actual variable names (See summary statitic example)

##Without round 7 and 6 (no negative autocorrelation, best model so far)

varMat1 <- matrix(c('average_totalinc_without.0','hermoney.0','hhpurchases.0','psychwellbeing_1.0','psychwellbeing_2.0','psychwellbeing_3.0','psychwellbeing_5.0',
                    'average_totalinc_without.1',NA,NA,'psychwellbeing_1.1','psychwellbeing_2.1','psychwellbeing_3.1','psychwellbeing_5.1',
                    'average_totalinc_without.2','hermoney.2','hhpurchases.2',NA,NA,NA,NA,
                    'average_totalinc_without.3','hermoney.3','hhpurchases.3',NA,NA,NA,NA,
                    'average_totalinc_without.4','hermoney.4','hhpurchases.4','psychwellbeing_1.4','psychwellbeing_2.4','psychwellbeing_3.4','psychwellbeing_5.4',
                    'average_totalinc_without.5','hermoney.5','hhpurchases.5','psychwellbeing_1.5','psychwellbeing_2.5','psychwellbeing_3.5','psychwellbeing_5.5',
                    'average_totalinc_without.8','hermoney.8','hhpurchases.8','psychwellbeing_1.8','psychwellbeing_2.8','psychwellbeing_3.8','psychwellbeing_5.8'),7,7, byrow = F) 


rownames(varMat1) <- c("Income", "hermoney", "hhpurchases","psychwellbeing_1", "psychwellbeing_2", "psychwellbeing_3", "psychwellbeing_5")

#Model 1
model2 <- panelgvar(data = Empowerment_wide,
  vars = varMat1, estimator = "FIML", missing = "pairwise")

# Run model:
model2 <- model2 %>% runmodel

# Check fit:
model2 %>% fit 

# Estimation algorithm (prune step):
model_prune2 <- model2 %>% prune(alpha = 0.05, recursive = FALSE)

##Stepup
model_pruneSP2 <- model_prune2 %>%  stepup(alpha = 0.05, criterion = "bic")

model_pruneSP2 %>% fit


# Compare:
comp <- compare(
  original = model2,
  pruned = model_pruneSP2
  )

# Differences:
comp$AIC[1] 
comp$AIC[2]

comp$BIC[1]
comp$BIC[2]

temporal <- getmatrix(model_pruneSP2, "PDC")
contemporaneous <- getmatrix(model_pruneSP2, "omega_zeta_within")
between <- getmatrix(model_pruneSP2, "omega_zeta_between")

# Average layout:
Layout <- averageLayout(temporal,contemporaneous,between)


# Plot all graphs:
max <- max(c(abs(temporal),abs(contemporaneous),abs(between)))


fig1 <- qgraph(temporal, labels = c("Income", "hermoney", "hhpurchases","WB_1", "WB_2", "WB_3", "WB_5"), title = "Temporal", label.cex = 1, layout = Layout)
fig2 <- qgraph(contemporaneous, labels = c("Income", "hermoney", "hhpurchases","WB_1", "WB_2", "WB_3", "WB_5"), title = "Contemporaneous",label.cex = 1, layout = Layout)
fig3 <-qgraph(between,labels = c("Income", "hermoney", "hhpurchases","WB_1", "WB_2", "WB_3", "WB_5"), title = "Between Subjects",label.cex = 1, layout = Layout)


png('temporalna.png',height = 10, width = 7, units = 'cm', res = 600)
plot(fig1)
dev.off()


png('contemporaneousna.png',height = 10, width = 7, units = 'cm', res = 600)
plot(fig2)
dev.off()


png('betweenna.png',height = 10, width = 7, units = 'cm', res = 600)
plot(fig3)
dev.off()


```



 
### Robustness Check
```{r}
### Create sum scores (for the plot and the descriptives)
#Psychwellbeing
index <- which(colnames(All_Rwanda_complete) %in% c("psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_4","psychwellbeing_5","psychwellbeing_6","psychwellbeing2_1", "psychwellbeing2_2","psychwellbeing2_3","psychwellbeing2_4","psychwellbeing2_5","psychwellbeing2_6"))

All_Rwanda_complete$PsychologicalWellbeingScaleFull <- rowSums(All_Rwanda_complete[,index])

index <- c("psychwellbeing_1","psychwellbeing_2","psychwellbeing_3","psychwellbeing_5")

All_Rwanda_complete$PsychologicalWellbeingScale <- rowSums(All_Rwanda_complete[,index])


#Social Support
index <- which(colnames(All_Rwanda_complete) %in% c("socialsupport_1","socialsupport_2","socialsupport_3","socialsupport_4"))
All_Rwanda_complete$SocialSupportScaleFull <- rowSums(All_Rwanda_complete[,index])


#Empowerment
index <- which(colnames(All_Rwanda_complete) %in% c("decisionmaking_1","decisionmaking_2","decisionmaking_4","decisionmaking_3","hermoney","hismoney","hhpurchases","decisionfam"))
All_Rwanda_complete$EmpowermentScaleFull <- rowSums(All_Rwanda_complete[,index])

index <- which(colnames(All_Rwanda_complete) %in% c("hermoney","hhpurchases"))
All_Rwanda_complete$EmpowermentScale <- rowSums(All_Rwanda_complete[,index])


#Stereotypes
index <- which(colnames(All_Rwanda_complete) %in% c("stereotypes_1","stereotypes_2","stereotypes_3","stereotypes_4"))
All_Rwanda_complete$StereotypesScaleFull <- rowSums(All_Rwanda_complete[,index])
```


```{r}

All_Rwanda_complete$Rround[All_Rwanda_complete$Rround == 100] <- 8


```

### Robustness Check
```{r}
All_Rwanda_lm <- All_Rwanda_complete
All_Rwanda_lm[,-c(1:2,4,5)] <- scale(All_Rwanda_complete[,-c(1:2,4,5)], center = F) 

#Dependent: PsychologicalWellbeingScale,EmpowermentScale

#Independent
#Rround, average_totalinc_without
#Cstartdate,Rgroupnr, ID_NR_VU

###INCOME
fit1 <- lm(InflationAverage_totalinc_without ~ Rround + as.factor(Cstartdate), All_Rwanda_lm)

###EMPOWERMENT
fit2 <- lm(EmpowermentScale ~ Rround + InflationAverage_totalinc_without + as.factor(Cstartdate), All_Rwanda_lm)


###PSYCHOLOGICAL WELLBEING
fit3 <- lm(PsychologicalWellbeingScale ~ InflationAverage_totalinc_without + EmpowermentScale + Rround + as.factor(Cstartdate), All_Rwanda_lm)

###TABLE
fit1_table1 <- invisible(stargazer(fit1, fit2, fit3, type = "html", omit = "Cstartdate", add.lines = list(c("Calendar Month Dummy", "Yes", "Yes", "Yes"))))

###############SUBSAMPLE################
########################################


###SOCIAL SUPPORT
fit4 <- lm(SocialSupportScaleFull ~ Rround, All_Rwanda_lm)

###EMPOWERMENT
fit5 <- lm(EmpowermentScaleFull ~ SocialSupportScaleFull + Rround, All_Rwanda_lm)

fit6 <- lm(EmpowermentScaleFull ~ SocialSupportScaleFull + Rround + StereotypesScaleFull, All_Rwanda_lm)

###MENTAL WELLBEING
fit7 <- lm(PsychologicalWellbeingScaleFull ~ EmpowermentScaleFull + SocialSupportScaleFull + Rround, All_Rwanda_lm)

fit8 <- lm(PsychologicalWellbeingScaleFull ~ EmpowermentScaleFull + SocialSupportScaleFull + StereotypesScaleFull + Rround, All_Rwanda_lm)

fit10 <- lm(PsychologicalWellbeingScaleFull ~ EmpowermentScaleFull*StereotypesScaleFull + SocialSupportScaleFull + Rround, All_Rwanda_lm)


###STEREOTYPES
fit9 <- lm(StereotypesScaleFull ~ SocialSupportScaleFull + Rround, All_Rwanda_lm)

###TABLE
fit2_table1 <- invisible(stargazer(fit4, fit5, fit6, fit7, fit8, fit9, type = "html", order=c("Rround", "SocialSupportScaleFull","EmpowermentScaleFull","StereotypesScaleFull")))

```